Quantum Semiprime Factorization: Leveraging Grover's Algorithm for Efficient Prime Decomposition

### 2025-03-27 LaTeX/paper.tex
Update citation

This work is still in progress, but we have a working implementation of Grover's 
algorithm with the CUDA-Q simulation which can estimate the time to factor any 
semiprime up to the current scaling limits of the CUDA-Q simulation.

>>>>

This work is still in progress, but we have a working implementation of Grover's 
algorithm with the CUDA-Q simulation which can estimate the time to factor any 
semiprime up to the current scaling limits of the CUDA-Q simulation\cite{quantumfactoring_github}.
